Sound and Automated Synthesis of Digital Controllers for Continuous Plants

### 2017-03-13 slides/presentation.tex
pres

\title {Sound and Automated Synthesis of Digital
Stabilizing Controllers for Continuous Plants}

@@

@@

\begin{frame}{\tool}
%
Modern control is implemented with digital microcontrollers, embedded within
a dynamical plant that represents physical components.
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/step1_figureB.png}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/step1_figureC.png}
    \end{subfigure}
     ~
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/step1_figureD.png}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.15\textwidth}
        \includegraphics[width=\textwidth]{figures/step1_figureA.png}
    \end{subfigure}
\end{figure}

>>>>

\title {Sound and Automated Synthesis of Digital Controllers for Continuous Plants}

@@

\date{March 2017}

@@

\begin{frame}{Cyber-Physical Systems}
%
\begin{itemize}
\item 
modern controls are implemented with digital microcontrollers, 
embedded within dynamical plants representing physical components 
\end{itemize}

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/step1_figureB.png}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/step1_figureC.png}
    \end{subfigure}
%     ~
%    \begin{subfigure}[b]{0.3\textwidth}
%        \includegraphics[width=\textwidth]{figures/step1_figureD.png}
%    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/step1_figureA.png}
    \end{subfigure}
\end{figure}
